|

### 2016-05-04 itraquant/Benchmark/itraq-benchmark.Rmd
benchmark results

Using the `quantify` function from MSnBase, with parameters `mehod=max, verbose=FALSE, strict=FALSE`, resulting:

@@

Repeating the same process for all of peptides with e-value < 50

>>>>

Using the `quantify` function from MSnBase, with parameters `method=``r quant_method`, `verbose=FALSE, strict=FALSE`, resulting:

@@

Repeating the same process for all of peptides with e-value < `r evalue_treshold`.
